On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains

### 2020-06-18 paper_lap/JCP_response1/01intro.tex
minor edits

 In this paper we describe a method for solving Laplace's equation on polygonal domains with Neumann boundary conditions given only a discretization of a corresponding Dirichlet problem. Our approach is based on using the discretization of a suitable adjoint problem. In particular, we show that if the transpose of the discretization of a suitable Dirichlet BIE is used, then the resulting solution will be accurate in a ``weak sense''; namely, it can be used to compute inner products with smooth functions accurately, though it cannot be interpolated. We then show how this solution can be used to obtain accurate solutions to the Neumann problem arbitrarily close to a corner by solving a set of local subproblems in the vicinity of that corner. \upd{This approach generalizes naturally to three-dimensional problems, though efficient discretization of the corresponding Dirichlet problems is the subject of ongoing research. A similar analysis as in \cite{} can be used to characterize the singularities along edges and near vertices, though there are a few challenges which prevent the immediate application of this analysis to the design of suitable discretizations.}

>>>>

 In this paper we describe a method for solving Laplace's equation on polygonal domains with Neumann boundary conditions given only a discretization of a corresponding Dirichlet problem. Our approach is based on using the discretization of a suitable adjoint problem. In particular, we show that if the transpose of the discretization of a suitable Dirichlet BIE is used, then the resulting solution will be accurate in a ``weak sense''; namely, it can be used to compute inner products with smooth functions accurately, though it cannot be interpolated. We then show how this solution can be used to obtain accurate solutions to the Neumann problem arbitrarily close to a corner by solving a set of local subproblems in the vicinity of that corner. \upd{This approach generalizes naturally to three-dimensional problems, though efficient discretization of the corresponding Dirichlet problems is the subject of ongoing research. A similar analysis as in \cite{serkhacha} can be used to characterize the singularities along edges and near vertices, though there are a few challenges which prevent the immediate application of this analysis to the design of suitable discretizations.}

### 2020-06-18 paper_lap/JCP_response1/03bvp.tex
minor edits

The following theorems {\color{olive}(see \cite{kress1989linear})} describe the behavior of the single and double layer potentials in the vicinity of the boundary curve $\Gamma.$

@@

\upd{
\begin{remark}
We note that the smoothness of the kernel $k$ for well-separated portions of the domain guarantees that the problem of determining the singularities arising in the vicinity of a corner for a polygonal domain can be reduced to the analysis of the wedge case, see the discussion in \cite{} for example.
\end{remark}
}

>>>>

The following theorems {\color{blue}(see for example \cite{kress1989linear})} describe the behavior of the single and double layer potentials in the vicinity of the boundary curve $\Gamma.$

@@

\upd{
\begin{remark}
We note that the smoothness of the kernel $k$ for well-separated portions of the domain guarantees that the problem of determining the singularities arising in the vicinity of a corner for a polygonal domain can be reduced to the analysis of the wedge case, see the discussion in \cite{hoskins2019numerical,serkhrachh} for example.
\end{remark}
}
